Review of Assigned Readings

### 2017-12-28 documentation/documentation.tex
added section 2.2 about STATA

\subsection{Stata}
(Dimitri's Part: stata version and anything else required to do your calculations)

>>>>

\subsection{Stata}
For the data analysis, we used the statistical software STATA (version 14.2). When seeking for statistical analysis, regression analysis or data management, STATA is a capable tool. To reproduce our results, you need to have the STATA software installed in your local computer and after starting the program you can follow the guidelines in chapter 4 (data analysis).
